---
title: "lab4_part2_po"
author: "Peter Omasta"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is going to be the new r markdown file for my new proejct that I am working on as a part of the second part of the forth lab for ESM 206. We will create a graph and a table in this document. 

-Interactive Plots: (plotly)
- Interactive tables: (DT)


```{r, message = FALSE, include=FALSE}
#here is some text that I put in here to attach packages

library(tidyverse)
library(tidyr)
library(plotly)
library(DT)
library(janitor)
```

Next we are going to read in the disease_burden.csv file to work on getting the data wrangled to create a graph and table that are interactive. 

```{r}

disease <- read_csv("disease_burden.csv")

#I want to clean this up with the janitor package. 

diseaseclean <- disease %>% 
  clean_names()
```

#The lab went a different direction than I thought, now I will be reading in the iris data set. This is a famous data set created by Edgar Anderson. 


```{r, echo=FALSE, include = FALSE}

iris_graph <- ggplot(data=iris, aes(x=Petal.Width,
                                    y= Petal.Length)) +
  geom_point()

iris_graph

#Does not lok great so lets make some aesthetic updates
```



```{r}
iris_graph2 <- ggplot(data=iris, aes(x=Petal.Width,
                                    y= Petal.Length)) +
  geom_point(aes(size= Sepal.Width,
                 color= Species),
             alpha=0.5) +
  theme_minimal() +
  labs(x= "Petal width (cm)",
       y= "Petal length (cm)",
       title = "Relationship of Petal Length and Width by Iris Species")

#iris_graph2

#Now we will make this an interactive plot by using ggplotly on this saved graph

ggplotly(iris_graph2)

#Super cool, can zoom in or out. Points are highlighted. 


```


That was a great stopping point, we already saved them to github so we can continue. Time for an interactive table using DT.

We wil be using the msleep file.

```{r}

datatable(msleep)
```







